---
title: "MMR studies 1"
author: "Henrique Laurino"
date: "December 9, 2016"
output: word_document
---



What we learned:
 - use other methods
 - final recommendation telling to use MORE DATA

**Intro**

our idea, bla bla bla, get this shit together and predict team interaction


**Data cleaning**


First, crunch player statistics in standardized variables

```{r}
rm(list=ls())
##read data 
results <- read.csv("focal_results.csv", stringsAsFactors=FALSE, quote = "")

##format variables
names(results)
results = results[,-c(1,3,5,8,23,31)]

results$round_id = as.character(results$round_id)
results$total_score = as.integer(results$total_score)
results$combat_score = as.integer(results$combat_score)
results$deathCnt = as.integer(results$deathCnt)
results$assultFlg = as.integer(results$assultFlg)
results$reconFlg = as.integer(results$reconFlg)
results$engineerFlg = as.integer(results$engineerFlg)
results$supportFlg = as.integer(results$supportFlg)
results$armoredLandFlg = as.integer(results$armoredLandFlg)
results$unarmoredLandFlg = as.integer(results$unarmoredLandFlg)
results$jetFlg = as.integer(results$jetFlg)
results$helicopterFlg = as.integer(results$helicopterFlg)
results$boatFlg = as.integer(results$boatFlg)
results$roundComplete = as.integer(results$roundComplete)
results$team = as.integer(results$team)
results$winningTeam= as.integer(results$winningTeam)
results$attackerTeam= as.integer(results$attackerTeam)
results[is.na(results)] <- 0
results[is.null(results)] <- 0

length(results$user_account_id[(results$team == results$winningTeam)])
length(results$user_account_id[(results$team == 0)])

results$winner = as.numeric(results$team == results$winningTeam | results$team == 0)
results$attacker = as.numeric(results$team == results$attackerTeam | results$attackerTeam == 0)
results$round_start_date = as.Date(results$round_start_date)


#TEAM is almost ALL NAS
#team count looks uninteresting 
#completion seems useless
#game mode seems to be better captured by other variables instead of using 17 indicators. Same for map, with 29 levels


##make training player statistics table
results$winner = as.factor(results$winner)
dat = data.frame("player_id" = results$user_account_id)
for(i in  1:length(results$user_account_id)){
    dat$avg_score[i] = mean(results$total_score[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$avg_permanence[i] = mean(results$player_seconds[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])/
    mean(results$round_seconds[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$avg_combat_score = mean(results$combat_score[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$avg_kd =  mean(results$killCnt[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])/ mean(results$deathCnt[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$rank = results$rank_at_end[i]
  dat$assaultFlg = mean(results$assultFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$reconFlg = mean(results$reconFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$engineerFlg = mean(results$engineerFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$supportFlg = mean(results$supportFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$armoredLandFlg = mean(results$armoredLandFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$jetFlg = mean(results$jetFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$unarmoredLandFlg = mean(results$unarmoredLandFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$helicopterFlg = mean(results$helicopterFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$boatFlg = mean(results$boatFlg[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$attacker = mean(results$attacker[results$round_start_date <= results$round_start_date[i] 
                            & results$user_account_id== results$user_account_id[i]])
  dat$winner = results$winner[i]
}
dat <- do.call(data.frame,lapply(dat, function(x) replace(x, is.infinite(x),0)))
dat[is.na(dat)] <- 0 

index.train = sample(length(dat$player_id), 5000)
dat.train=dat[index.train,]
dat.test=dat[-index.train,]

```

HOLY SHIT, THIS WAS SO BORING!
From this, we develop a net to predict winning chance:

```{r}
library(h2o)

#start cluster
localH2O <- h2o.init(ip = "localhost", port = 54321, startH2O = TRUE)

#set h20 frames
train.h2o <- as.h2o(dat.train[, -1])
test.h2o <- as.h2o(dat.test[, -1])
summary(results$winner)
summary(dat.train$winner)
names(test.h2o)

############## how do we deal with all 1s

#build model and train
net.model = 
  h2o.deeplearning(x = 1:15, y = 16,
                   training_frame = train.h2o, validation_frame = test.h2o, standardize = TRUE,
                   activation = "TanhWithDropout", seed = 10,
                   input_dropout_ratio = 0.2,hidden_dropout_ratios = c(0.5,0.5,0.5),
                   hidden = c(50,50,50),epochs = 100, categorical_encoding = "Binary")

#reports
net.model

## Using the DNN model for predictions
h2o_yhat_test <- h2o.predict(model, test_h2o)

## Converting H2O format into data frame
df_yhat_test <- as.data.frame(h2o_yhat_test)

```


ALL METHODS:
  - random forest
  - pca
  - rotation forest
  - support vector machine
  - maxent
  - deep learning



Next, let's get the TEAM STATISTICS.

```{r}

#our problem

length(unique(results$round_id))/length(results$round_id)
# 99.7% unique results!

##subsetting: 5897 obs. 
set.seed(10)
index.train = sample(length(unique(results$round_id)), 5000)
results=results[index.train,]
results.test=results[-index.train,]
length(unique(results$round_id))

#make new team dataset by summing by round AND team
team.train = data.frame("round_id" = unique(results$round_id))
team.train

```



```{r}

##make training player statistics table
#id
individual.train = data.frame("id" = unique(results.train$user_account_id))
#average permanence
individual.train$avg_permanence = (aggregate(player_seconds ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]/aggregate(round_seconds ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1])
#average total score
individual.train$avg_score = aggregate(total_score ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
#average combat score                        
individual.train$avg_combat_score = aggregate(combat_score ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
#agressivity(combat score/total score)
individual.train$aggressivity = individual.train$avg_combat_score/individual.train$avg_score
#average kills/deaths
individual.train$avg_kd = (aggregate(killCnt ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]/aggregate(deathCnt ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1])
#latest rank
individual.train$latest_rank = aggregate(rank_at_end ~ user_account_id, data = results.train, FUN = function(x) c(max(x)))[,-1]
#round count
individual.train$round_count = as.data.frame(table(results.train$user_account_id))[,-1]
#flag %
individual.train$assaultFlg = aggregate(assultFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
individual.train$reconFlg = aggregate(reconFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
individual.train$engineerFlg = aggregate(engineerFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
individual.train$supportFlg = aggregate(supportFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
individual.train$armoredLandFlg = aggregate(armoredLandFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
individual.train$jetFlg = aggregate(jetFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]  
individual.train$unarmoredLandFlg = aggregate(unarmoredLandFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1] 
individual.train$helicopterFlg = aggregate(helicopterFlg ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]  
individual.train$boatFlg = aggregate(boatFlg~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]  
#attacker %
individual.train$attacker = aggregate(attacker ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
#win%
individual.train$winner = aggregate(winner ~ user_account_id, data = results.train, FUN = function(x) c(mean(x)))[,-1]
#final clean
individual.train <- do.call(data.frame,lapply(individual.train, function(x) replace(x, is.infinite(x),0)))
individual.train[is.na(individual.train)] <- 0     

### Now for test data:
individual.test = data.frame("id" = unique(results.test$user_account_id))
individual.test$avg_permanence = (aggregate(player_seconds ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]/aggregate(round_seconds ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1])
individual.test$avg_score = aggregate(total_score ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$avg_combat_score = aggregate(combat_score ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$aggressivity = individual.test$avg_combat_score/individual.test$avg_score
individual.test$avg_kd = (aggregate(killCnt ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]/aggregate(deathCnt ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1])
individual.test$latest_rank = aggregate(rank_at_end ~ user_account_id, data = results.test, FUN = function(x) c(max(x)))[,-1]
individual.test$round_count = as.data.frame(table(results.test$user_account_id))[,-1]
individual.test$assaultFlg = aggregate(assultFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$reconFlg = aggregate(reconFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$engineerFlg = aggregate(engineerFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$supportFlg = aggregate(supportFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$armoredLandFlg = aggregate(armoredLandFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$jetFlg = aggregate(jetFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$unarmoredLandFlg = aggregate(unarmoredLandFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1] 
individual.test$helicopterFlg = aggregate(helicopterFlg ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]  
individual.test$boatFlg = aggregate(boatFlg~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]  
individual.test$attacker = aggregate(attacker ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test$winner = aggregate(winner ~ user_account_id, data = results.test, FUN = function(x) c(mean(x)))[,-1]
individual.test <- do.call(data.frame,lapply(individual.test, function(x) replace(x, is.infinite(x),0)))
individual.test[is.na(individual.test)] <- 0     

```